---
title: "Intro to R Markdown"
author: "ahill14"
date: "6/3/2019"
output:
  pdf_document: 
    toc: true
    number_sections: true
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown
This is a Markdown document in RStudio.   
You can "knit" it as an html, pdf, word, or slides, but the general layout remains the same. 
It is a great way to distribute finalized code and findings, especially on GitHub 
since there is a nice, GitHub compatible .md document that makes it easy to see and 
understand code/ research. 

# Code
Here is a chunk of code that I will include in my report: 
``` {r}
str(cars)
head(cars)
mean(cars$speed)
mean(cars$dist)
```
 
# Equations
You can also embed mathematical equations like this:  
Add 3 and 5: 
$$ 3 + 5 = 8 $$. 

# Displaying code
You can customize how code and results show up in your .Rmd.

* eval = FALSE shows code, doesn't evaluate so no results
* echo = FALSE hides code, shows results 
* message = FALSE hides messages, shows and evalutates code

For example. 

* eval = FALSE
``` {r eval = FALSE}
str(cars)
```
* echo = FALSE 
``` {r echo = FALSE}
str(cars)
```




